There should be a portal for the customers to leave suggestions and feedback and report problems. There also need to be an RMA, so customers can return the product if it's defective or they simply don't want it for a refund.
\subsection{Users shall be able to get support on any issues}
\subsubsection{Description}
The must be a website with a portal where customers can create a profile if they wish. Customers aren't require to have a profile if they preferred not to have a profile. Customer can also either leave a suggestion or a feedback for the app through the website or through the Google Play store. The portal on the website should have an FAQ section for questions that customers generally have about the app and the hydrometer.
\\
\\
There should be a community section where customers can discuss among themselves, the producers of the product, and the developers of the app about any issues, concerns, or questions. The customers should also be able to report any issues directly to us through the website and we should be able to address it with them if they wish. Customers should also be able to contact customer support through email or a hot line in case they have any issues, concerns, or questions.
\\
\\
We must be able to create an RMA (Return Merchandise Authorization) with any customers that have issues with their product. The RMA allows the customer to send the product back if it's having issues so we can repair it and send it back to them or we can send them a another one. Each customer has a full one-year warranty coverage on the product. The warranty policy will cover the cost of repairing or replacing the product if the product fails within the one-year period due to manufacturer defect.
\\
\\
Customers also have the option to return the product for a full refund within 30 days if whether the product failed or if the product failed to perform what the customers expected or even if the customers simply doesn't want the product.
\subsubsection{Source}
The source is from my own understanding of customer and technical support.
\subsubsection{Constraints}
The warranty will not cover repair or replacement cost of products if it becomes defective one-year after it had been shipped. The warranty will not cover damages that aren't caused by manufacturer defect.
\\
\\
If a customer wanted to return a product for a full refund just because they don't want it and that the customer couldn't provide us any proof of manufacturer defect or why the product doesn't perform as the customer expected. Then the customer will be required to pay a restocking fee for return the product.
\subsubsection{Standards}
This product is governed by Consumer Protection.
\subsubsection{Priority}
This requirement is somewhat important. It is not something we shall worry to much about, but it's important when the products failed to perform what the customers expected.